Spin canonical rings of log stacky curves

### 2015-07-15 curves-write-up/arXiv versions/spin-cring-arXiv-v2.tex
curves: minor edit intro, further qs

\begin{abstract}
 	Consider modular forms arising from a finite-area quotient of the
	upper-half plane by a Fuchsian group. By the classical results of
	Kodaira--Spencer, this space of modular forms may be viewed as the
	log spin canonical ring of a stacky curve. In this paper, we
	tightly bound the degrees of minimal generators and relations of
	log spin canonical rings. As a consequence, we obtain a tight bound
	on the degrees of minimal generators and relations for rings of
	modular forms of arbitrary integral weight.
\end{abstract}

@@

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian group}, i.e.~ a discrete subgroup of
$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations, such that $\Gamma \backslash \BH$ has
finite area.
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$.
One of the best ways to describe the ring $M(\Gamma)$ is to write
down a presentation.
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
We extend their result to all Fuchsian groups $\Gamma$ in the main
theorem of this work.

@@

\item One direction for further research is to extend the results
	of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx$, 
	where $nD \sim K.$ The canonical rings of such divisors often
	arise as rings of fractional weight $\frac{2}{n}$ modular forms.
	For more details on fractional weight modular forms, see Adler and
	Ramanan \cite[p. 96]{adler:moduli} and Milnor
	\cite[$\mathsection$ 6]{milnor:fractional-weight}.

>>>>

\begin{abstract}
 	Consider modular forms arising from a finite-area quotient of the
	upper-half plane by a Fuchsian group. By the classical results of
	Kodaira--Spencer, this ring of modular forms may be viewed as the
	log spin canonical ring of a stacky curve. In this paper, we
	tightly bound the degrees of minimal generators and relations of
	log spin canonical rings. As a consequence, we obtain a tight bound
	on the degrees of minimal generators and relations for rings of
	modular forms of arbitrary integral weight.
\end{abstract}

@@

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian group}, i.e.~ a discrete subgroup of
$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations, such that $\Gamma \backslash \BH$ has
finite area.
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$.
One of the best ways to describe the ring $M(\Gamma)$ is to write
down a presentation.
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
The main theorem of this work extends their result to all Fuchsian
groups $\Gamma$.

@@

\item One direction for further research is to extend the results
	of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx$, 
	where $nD \sim K$ for some integer $n$ greater than $2$. The
	canonical rings	of such divisors often arise as rings of
	fractional weight $\frac{2}{n}$ modular forms.
	For more details on fractional weight modular forms, see Adler and
	Ramanan \cite[p. 96]{adler:moduli} and Milnor
	\cite[$\mathsection$ 6]{milnor:fractional-weight}.
